### 2023-11-17 Scripts/Manuscript/manuscript.Rmd
included section references.

# Introduction

For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims. Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability]. In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating]. Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study. They found however, that in many instances the results did no match those of the original studies. This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].

@@

The structured coding protocol was used for both replication protocols and original studies. A series of questions relating to measurement practices and measurement error were used to extract the information. Descriptions of the extracted variables can be found in the Measures section below. The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections. Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information. An exception to this procedure was a question asking about the presence of example items. For this question, information from supplementary materials was uniquely considered as relevant. Another exception was the question regarding the replication of the original effect. Tables from the final report of each Many Labs project were used to answer that question.

<!-- @ref(sec:measures) didn't work for section cross-reference in the paragraph above-->

@@

## Measures

@@

### Exploratory Analyses

@@

The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the Exploratory Analyses section above. Suitable data for factor analyses was available for nineteen measures. These measures were the same as those shown in Figure \@ref(fig:Plot23AlphaCode), with the addition of one more measure from [@cacioppo1983effects]. A composite score based on the measurement responses was used for sixteen of the nineteen measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional. The number of dimensions for the remaining three were unclear. Sufficient fit of the unidimensional model was found for six out of the nineteen evaluated measures. However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model did not hold for any measure data based on the parallel analysis test alone. Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.

>>>>

# Introduction 
For many years, methodologists and statisticians have raised concerns about the way that research practices [@cumming2014new; @wicherts2016degrees], reporting practices [@bakker2011mis; @nuijten2016prevalence], and publication decisions [@sterling1959publication; @bakker2012rules; @giner2012science] may undermine the credibility of psychology's scientific claims. Replicability of a finding is seen as one crucial step in establishing its credibility [@nosek2022replicability]. In order to investigate the replicability of psychological science, the large scale Reproducibility Project: Psychology (RPP) was set-up [@osc2015estimating]. Replications of 100 published studies were performed using similar materials, procedures, and analyses, while using a new sample of participants for each study. They found however, that in many instances the results did no match those of the original studies. This lack of replicability of psychological findings illustrated that psychology was facing a so-called 'replication crisis' [@hughes2018psychology; @giner2019crisis].

@@

The structured coding protocol was used for both replication protocols and original studies. A series of questions relating to measurement practices and measurement error were used to extract the information. Descriptions of the extracted variables can be found in the [Measures](#Measures) section below. The scope of the coding was limited to the abstract, method, procedure, materials, measure, and initial parts of the results sections. Additionally, a keyword search using the name of the measured variable was used to search for any potentially missed information. An exception to this procedure was a question asking about the presence of example items. For this question, information from supplementary materials was uniquely considered as relevant. Another exception was the question regarding the replication of the original effect. Tables from the final report of each Many Labs project were used to answer that question.

@@

## Measures {#Measures}

@@

### Exploratory Analyses {#ExploratoryAnalyses}

@@

The unidimensionality of the measures used in the Many Labs projects was assessed through factor analyses, and evaluated based on the criteria discussed in the [Exploratory Analyses](#ExploratoryAnalyses) section above. Suitable data for factor analyses was available for nineteen measures. These measures were the same as those shown in Figure \@ref(fig:Plot23AlphaCode), with the addition of one more measure from [@cacioppo1983effects]. A composite score based on the measurement responses was used for sixteen of the nineteen measures to form a single variable in the analyses, and were thus regarded as intended to be unidimensional. The number of dimensions for the remaining three were unclear. Sufficient fit of the unidimensional model was found for six out of the nineteen evaluated measures. However, as shown in Table \@ref(tab:UnidimesnionalityTestResultsTable) the unidimensional model did not hold for any measure data based on the parallel analysis test alone. Only the RMSEA $< .08$ criteria suggested evidence for single factor structures.
